---
output: pdf_document
papersize: a4
---
**Name:** Jaswinderpal Singh\
**Class:** M.Sc. Statistics, Sem 1 \
**Roll No.** 32587   

# Sol. 5

## (a) To generate Random sample of size 30 from N(40,9) and arranging in Increasing order of magnitude 
## (b) To computer summary statistics of above data

```{r}
sp = rnorm(30,mean=40, sd=3) # random sample from N(40,9)
sort(sp) # arranging in increasing order of magnitude

#(b) Summary statistics
summary(sp)
```

## (c) To carry out correlation and regression analysis using R

```{r}
rba = c(3,5,8,4,7,10,2,1,6,9) #Judge A
rbb = c(6,4,9,8,1,2,3,10,5,7) #Judge B
cor(rba, rbb, method = "spearman") # Spearman's rank correlation
plot(rba,rbb, pch=20,col="blue4", xlab = "Judge A", ylab = "Judge B") #scatter plot
model = lm(rba~rbb) # Linear Regression model
summary(model)
coef(model)  # Coefficients
abline(model, col="red") # drawing regression equation
```

## (d) To apply t test in case of equal but unknown variances.

```{r}
dietA = c(10,6,16,17,13,12,8,14,14)
dietB = c(7,22,15,13,14,8,21,10,16,18)
#(i) and (ii)
t.test(dietA, dietB, var.equal = TRUE, conf.level=0.99)
```

## (e) To compute pdfs, cdfs, inverse cdfs and plots of distributions using R

```{r}
# pdf of chi-square
#(i)
dchisq(3,9)
#(ii)
dchisq(5,10)

x = seq(0,20,by=0.1)
y = dchisq(x,7)
plot(x,y, pch=20, col="blue4")
curve(dchisq(x,7),lwd=1.5,col="red",add=T)

# cdf of t distribution
#(i)
pt(3,5)
#(ii)
pt(0,7)

# inverse cdf of t distribution
#(i)
qt(0.3,8)
#(ii)
qt(0.6,8)
```

## (f) To solve Que 2(a) with R commands

```{r,warning=FALSE}
library(grid)
library(vcd)
mp = 0:5
f = c(139,76,28,4,2,1)
data = rep(mp,f)
gf = goodfit(data, type = "poisson", method = "MinChisq")
gf # fitting Poisson distribution
summary(gf) # Testing goodness of fit
```