---
output:
  pdf_document: default
  html_document: default
---
# Experiment 6  

**Name:** Jaswinderpal Singh\
**Class:** M.Sc. Statistics, Sem 1\
**Date:** 08 November 2021  
   
**1. Aim:** To Create a file with name ‘test’ using data frame having specified variables   

```{r}
data<-read.csv("test.csv")
attach(data)
data$sex[data$sex==1]<-"male"
data$sex[data$sex==2]<-"female"
data$mutation[data$mutation==1]<-"mutated"
data$mutation[data$mutation==0]<-"not mutated"
data$locality[data$locality==1]<-"rural"
data$locality[data$locality==2]<-"urban"
data$religion[data$religion==1]<-"hindu"
data$religion[data$religion==2]<-"muslim"
data$religion[data$religion==3]<-"sikh"
data$religion[data$religion==4]<-"chritian"
```
(a) To Use head and tail command to display the first 10 top and bottom observations along with variable name

```{r}
head(data,10)
tail(data,10)
```
(b) To Extract each variable individually from data frame   

```{r}
data$mutation
data$age
data$locality
data$sex
data$religion
```
c) Make a 2 x 2 table of gender and locality using ‘table’ command
```{r}
table<-table(sex,locality)
table
```
(d),(e) To find association between locality and gender using (i) Yule’s coefficient Q_AB, (ii) Coefficient of Colligation Y_AB, (iii) Coefficient V_AB. Interpret your result.
```{r}
#Yule's Coefficient
Q_AB = (19*5-11*15)/(19*5+11*15)
Q_AB
#Coefficient of colligation
Y_AB = (sqrt(19*5)-sqrt(11*15))/(sqrt(19*5)+sqrt(11*15))
Y_AB
#V_AB
V_AB = (19*5-11*15)/sqrt(30*20*34*16)
```
(f) Identifying the structure of your file using ‘str’ command and dimensional of file using ‘dim’ command
```{r}
str(data)
dim(data)
```
\newpage  
**2. Aim:** To Generate given vectors a,b,c. Combine them in vector‘d’ using (i) data frame (ii) list, and observe the difference (iii) identify the class of ‘d’
```{r}
a<-c(34,35,36,39)
b<-c(15,14,37,45)
c<-c(1,2)  
d<-data.frame(a,b,c)
d
d1<-list(a,b,c)
d1
class(d)
class(d1)
```
\newpage
**3. Aim:** To generate matrices A and B and carry out matrix computations
```{r}
A<-matrix(c(11,14,19,24,25,29,30,35,39),nrow=3,byrow=3)
A
B<-matrix(c(8, 9, 10, 11,14,13, 20, 22, 28),nrow=3,ncol=3 )
B
#(i)
A+B
#(ii)
A%*%B
#(iii)
A*B
#(iv)
det(A)
#(v)
diag(B)
#(vi) Transpose of A
A
t(A)
#(vii) Inverse of A and B matrices
A
# inverse of A
solve(A)
B
# inverse of B
solve(B)
#(viii)
library(Matrix)
eigen(A)
#(ix)
rank(A)
rankMatrix(A)
```
\newpage
**4. Aim**   
(a) To Generate a 3 x 4 matrix ‘C’ with all elements 5.
```{r}
C<-matrix(c(5),nrow=3,ncol=4)
C
```
(b) Generate 5 x 4 matrix ‘D’ with elements 1:20.
```{r}
D<-matrix(1:20,nrow=5,ncol=4)
D
```