---
output:
  pdf_document: default
  html_document: default
---

# Experiment 11

**Name:** Jaswinderpal Singh\
**Class:** M.Sc. Statistics, Sem 1\
**Date:** December 6, 2021

## **3. Aim:** To Generate a random sample from binomial distribution and test the goodness of fit.

```{r,warning=FALSE}
library(grid)
library(vcd)
x = rbinom(350,10,0.5)
table(x)
gf = goodfit(x,type="binomial",method="MinChisq")
summary(gf)
```

## **4. Aim:** To Generate a random sample from Poisson distribution and test the goodness of fit.

```{r,warning=FALSE}
y = rpois(300,5)
table(y)
Gf = goodfit(y,type="pois",method="MinChisq")
summary(Gf)
```

\newpage

## **5. Aim:** To Generate a sample size 100 between 1:10 with replacement and check whether Binomial or Poisson distribution fits well to this data.

```{r,warning=FALSE}
z = sample(1:10,100,replace = T)
table(z)
summary(goodfit(z,type="binomial",method = "MinChisq"))
summary(goodfit(z,type="pois",method = "MinChisq"))
```

## **6. Aim:** To Check the normality of the given data using (i) Shapiro-Wilk normality test (ii) Anderson-darling test, and (iii) normal quantile plot (Q-Q plot).

```{r}
library(nortest)
h = c(40,26,39,14,42,18,25,43,46,27,15,44,40,38,31,
46,52,25,35,35,19,47,19,26,35,44,48,32,30,20,33,29,
34,41,43,18,35,30,14,26,43,22,33,44,45,36,39,31,12,
29)

# Define
# H_0: Data follows Normal Distribution
# H_1: Data does not follow Normal Distribution

# (i) Shapiro-Wilk normality test
shapiro.test(h)

# (ii) Anderson Daring Test
ad.test(h)

# (iii) normal quantile plot (Q-Q plot)
qqnorm(h, col="blue4",pch = 20)
qqline(h, col="magenta",lwd = 1.5)
grid()
```
$H_0$ is accepted.
