---
output:
  pdf_document: default
  html_document: default
---

# Experiment 12

**Name:** Jaswinderpal Singh\
**Class:** M.Sc. Statistics, Sem 1\
**Date:** December 8, 2021

## **2. Aim:** To test whether population mean is equal to \$10 at 5% level of significance.

*Define* $$H_0 : \mu = 10$$\
$$H_1 : \mu \neq 10$$

```{r}
n = 64
sig = 6
xbar = 12

Z = (xbar - 10)/(sig/sqrt(n))  # Z Statistic
Z

# Critical Values two sided
c(qnorm(0.05/2),qnorm(0.05/2,lower.tail = F)) 

# 95% confidence interval
c(xbar- qnorm(0.05/2,lower.tail = F)*(sig/sqrt(n)),
xbar+ qnorm(0.05/2,lower.tail = F)*(sig/sqrt(n))) 
```

Here $$|Z| > z_{\alpha/2} $$\
$\therefore H_0$ is rejected.

\newpage

## **3. Aim:** To test the difference of two population means at 1% level of significance.

*Define*\
$$H_0 : \mu_1 = \mu_2$$\
$$H_1 : \mu_1 \neq \mu_2$$

```{r}
n1 = 400
n2 = 400
x1bar = 250
x2bar = 220
sig1 = 40
sig2 = 55
SE = sqrt(sig1^2/n1 + sig2^2/n2)  # Standard Error

Z1 = ((x1bar - x2bar)-0) /SE  # Z Statistic
Z1

# two sided
# Critical Value at 5% level of significance
c(qnorm(0.01/2),qnorm(0.01/2,lower.tail = F)) 

# 99% confidence interval
c((x1bar - x2bar)- qnorm(0.01/2,lower.tail = F)*SE,
(x1bar - x2bar)+ qnorm(0.01/2,lower.tail = F)*SE) 
```

Here $$|Z| > z_{\alpha /2}$$\
$\therefore H_0$ is rejected.\
\newpage

## **4. Aim:** To test whether population proportion is more than 80% at 5% level of significance

*Define*\
$$H_0 : P = 0.80$$\
$$H_1 : P > 0.80$$

```{r}
P = 0.80
Q = 1-P
X = 18
n3 = 20
p = X/n3
Z2 = (p-P)/sqrt(P*Q/n3)   # Z Statistic
Z2

# right tailed
# Critical Values at 5% level of significance
qnorm(0.05, lower.tail = F)
```

Here $$Z < z_\alpha$$\
$\therefore H_0$ is accepted.\
\newpage

## **5. Aim:** To test whether the difference between two proportions is significant

*Define*\
$$H_0 : P_1 = P_2$$\
$$H_0 : P_1 \neq P_2$$

```{r}
n3 = 900
n4 = 1600
p1 = 0.30
p2 = 0.18
P_hat = (n3*p1+n4*p2)/(n3+n4)
Q_hat = 1- P_hat
se = sqrt(P_hat*Q_hat*(1/n3 + 1/n4))
  
Z3 = (p1-p2)/se  # Z Statistic
Z3

# two sided
# Critical Value at 5% level of significance
c(qnorm(0.05/2), qnorm(0.05/2, lower.tail = F))

# 95% Confidence Interval
c((p1 - p2) - qnorm(0.05/2, lower.tail = F)*se,
(p1 - p2) + qnorm(0.05/2, lower.tail = F)*se)
```

Here $$|Z| > z_{\alpha/2}$$\
$\therefore H_0$ is rejected.
