---
output:
  pdf_document: default
  html_document: default
---

# Experiment 3

**Name:** Jaswinderpal Singh\
**Class:** M.Sc. Statistics, Sem 1\
**Date:** October 18, 2021\

**1. Aim:** To calculate Karl Pearson and Spearman's correlation coefficients and to draw scatter plot for given data.

*Calculations:*

```{r}
paper1 = c(45,55,60,58,60,65,68,70,75,80,85)
paper2 = c(56,50,82,60,62,64,65,70,74,82,90)
cor(paper1,paper2,method="pearson")  #Karl Pearson correlation coefficient
cor(paper1,paper2,method="spearman")  #Spearman’s rank correlation coefficient
plot(paper1,paper2, main = "Scatter Plot", col="blue4",pch=20)
grid()
```
  
\newpage

**3. Aim:** To find regression equation, create scatter plot and other computations using R

*Calculations:*

```{r}
x = c(39,65,62,90,82,75,25,98,36,78)
y = c(47,53,58,86,62,68,60,91,51,84)
#(a) To Find the regression equation of sales on advertisement expenses.
yonx = lm(y~x)
summary(yonx)
coef(yonx)   
```

Hence, regression equation is $Y = 33.4397925 + 0.5009263*x$

```{r}
#(b) To Calculate the sales when an advertisement expense is 25.
yat25 = 33.4397925+0.5009263*25 # Sales when expenditure is 25
yat25

#(c) Draw a scatter plot along with regression line.
plot(x,y, main="Scatter Plot", xlab="expenses", ylab="sales",col="blue",pch=20)
abline(33.4397925,0.5009263,col="red") #or abline(yonx)
```

\newpage

**4. Aim:** To calculate BMI using R

*Calculations:*

```{r}
wt = c(60,72,57,90,85)
ht = c(1.75,1.80,1.65,1.90,1.85)
bmi = wt/ht^2
bmi
```
 
**5. Aim:** To generate sequences using R

*Calculations:*

```{r}
#(i) To Generate a sequence from 1 to 20.
1:20   

#(ii) To Generate a sequence from 1 to 40 with increment of 2.
seq(1,40,2)   

#(iii) To Generate a sequence from 1 to 20 and then 30 to 40.
c(1:20,30:40)
```
