---
output:
  pdf_document: default
  html_document: default
---


# Experiment 1

**Name:** Jaswinderpal Singh\
**Class:** M.Sc. Statistics, Sem 1\
**Date:** October 6, 2021

## 1(b) **Aim:** To construct histogram and Stem & leaf display of given data using R

*Calculations:*

```{r}
z = c(76,57,74,100,73,77,88,77,51,62,149,86,57,72,
      67,54,54,91,62,44,66,55,95,71,73,57,51,114,61,
      42,78, 53,106,35,85,72,61,72,41,59,63,54,59,128
      ,67,83,95,88,109,79,58,82,153,84,62,70,44,61,55,
      69,59,50)
hist(z,main="Histogram of BAL", col = "green4", border = "white")
```

\newpage

```{r}
stem(z)
```

## 1(c) **Aim:** To Compute Mean, Median, Q1, Q3, Geometric Mean and Harmonic Mean for given data using R.

*Calculations:*

```{r}
mean(z)
median(z)
Q1 = quantile(z,0.25)
Q1
Q3 = quantile(z,0.75)
Q3
library(psych)
geometric.mean(z)
harmonic.mean(z)
```

\newpage

## 2. **Aim:** To generate the given vector, store it in x and carry out computations.

*Calculations:*

```{r}
x = c(1, 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5, 6, 12, 24, 15, 20)
x
```

#### (a) Mean, Median, Mode, Quartiles, Range, Standard deviation, Variance, Coefficient of variation

```{r}
mean(x)
median(x)
# Since every value occurs with single frequency,therefore mode doesn't exist
Q1 = quantile(x,0.25)
Q2 = quantile(x,0.50)
Q3 = quantile(x,0.75)
Q1
Q2
Q3
(Range = max(x)-min(x))
sd(x)
var(x)
(cv = sd(x)/mean(x)*100)
```

#### (b) Summary

```{r}
summary(x)
```

#### (c) Sort ascending

```{r}
sort(x)
```

#### (d) Sort descending

```{r}
sort(x,decreasing = T)
```

#### (e) Order an index and check whether this is same as x[order(x)].

```{r}
order(x)
x[order(x)]
```

\newpage

### Further computations

#### (a) **Aim:** To compute log(x), log(x) to base 10, log(x) to base 2, 3+log(x), sum(x), sin(x), tan(x), gamma(x), lgamma(x)   
   
```{r}
log(x)
log10(x)
log2(x)
3+log(x)
sum(x)
sin(x)
tan(x)
gamma(x)
lgamma(x)
```

#### **(b) Aim:** To Compute x\^3, store in y, extract second element, (2,4)th element and elements from 2 to 7   

```{r}
y = x^3
y
y[2]
y[c(2,4)]
y[2:7]
```

\newpage

#### **(c) Aim:** To Generate a vector with marks of 5 students and then draw a Bar diagram   
   
```{r}
marks = c(45,65,55,98,76)
marks
names(marks) = c("A","B","C","D","E")
barplot(marks, col="purple", border="black")
```
