---
output:
  pdf_document: default
  html_document: default
---

# Experiment 2

**Name:** Jaswinderpal Singh\
**Class:** M.Sc. Statistics, Sem 1\
**Date:** October 13, 2021

## 2. **Aim:** Generate a vector of given observations Using R, compute first four central order moments, skewness and kurtosis.

*Calculations:*

```{r}
 v = c(56,61,57,77,62,75,63,55,64,60,
       60,57,61,57,67,62,69,67,68,59,
       65,72,65,61,68,73,65,62,75,80)
 v
 # Compute first 4 central moments, skewness, kurtosis
 vbar = mean(v)
(m1 = sum(v-vbar)/length(v))  # first central moment 
(m2 = sum((v-vbar)^2)/length(v))  # second central moment 
(m3 = sum((v-vbar)^3)/length(v)) # third central moment 
(m4 = sum((v-vbar)^4)/length(v)) # fourth central moment 

#skewness
sk = (m3^2)/(m2^3)
sk   #positively skewed
#kurtosis
ku = m4/(m2^2) - 3
ku   #platy-kurtic
```

\newpage

## 3. **Aim:** Generate a random sample of 100 observations between 1 to 10 and count the frequency of each factor i.e. 1 to 10 using R. Also draw Bar-plot of the generated frequency table

*Calculations:*

```{r}
d = sample(c(1:10),100,replace=T)
d # Random Sample
table(d) # Counting frequency
barplot(table(d), col="green4") 
```
